Combined annotation exploration for SCPCP000006

### 2024-11-01 analyses/cell-type-wilms-tumor-06/notebook/07_combined_annotation_across_samples_exploration.Rmd
Found infercnv argument to get infercnv running for the sample with the missing annotations, and updated code accordingly to run this sample

      # Read in the Seurat object
      if (file.exists(input_file)) {
        srat <- readRDS(input_file)

@@

          # cnv global estimation per chromosome
          has_cnv_chr1 = srat$has_cnv_chr1,
          has_cnv_chr2 = srat$has_cnv_chr2,
          has_cnv_chr3 = srat$has_cnv_chr3,
          has_cnv_chr4 = srat$has_cnv_chr4,
          has_cnv_chr5 = srat$has_cnv_chr5,
          has_cnv_chr6 = srat$has_cnv_chr6,
          has_cnv_chr7 = srat$has_cnv_chr7,
          has_cnv_chr8 = srat$has_cnv_chr8,
          has_cnv_chr9 = srat$has_cnv_chr9,
          has_cnv_chr10 = srat$has_cnv_chr10,
          has_cnv_chr11 = srat$has_cnv_chr11,
          has_cnv_chr12 = srat$has_cnv_chr12,
          has_cnv_chr13 = srat$has_cnv_chr13,
          has_cnv_chr14 = srat$has_cnv_chr14,
          has_cnv_chr15 = srat$has_cnv_chr15,
          has_cnv_chr16 = srat$has_cnv_chr16,
          has_cnv_chr17 = srat$has_cnv_chr17,
          has_cnv_chr18 = srat$has_cnv_chr18,
          has_cnv_chr19 = srat$has_cnv_chr19,
          has_cnv_chr20 = srat$has_cnv_chr20,
          has_cnv_chr21 = srat$has_cnv_chr21,
          has_cnv_chr22 = srat$has_cnv_chr22
        ) |>
          tibble::rownames_to_column("barcode") |>
          dplyr::mutate(sample_id = sample_id)
      }
    }
  ) |>
  # now combine all dataframes to make one big one
  dplyr::bind_rows()
```

@@

- Combining label transfer and CNV inference we annotated 39/40 Wilms tumor samples in SCPCP000006. For the remaining samples (SCPCS000203), we need to investigate inferCNV further, since for some reason inferCNV removes cells from the inference and errors.

>>>>

      # Read in the Seurat object
      srat <- readRDS(input_file)

@@

        # cnv global estimation per chromosome
        has_cnv_chr1 = srat$has_cnv_chr1,
        has_cnv_chr2 = srat$has_cnv_chr2,
        has_cnv_chr3 = srat$has_cnv_chr3,
        has_cnv_chr4 = srat$has_cnv_chr4,
        has_cnv_chr5 = srat$has_cnv_chr5,
        has_cnv_chr6 = srat$has_cnv_chr6,
        has_cnv_chr7 = srat$has_cnv_chr7,
        has_cnv_chr8 = srat$has_cnv_chr8,
        has_cnv_chr9 = srat$has_cnv_chr9,
        has_cnv_chr10 = srat$has_cnv_chr10,
        has_cnv_chr11 = srat$has_cnv_chr11,
        has_cnv_chr12 = srat$has_cnv_chr12,
        has_cnv_chr13 = srat$has_cnv_chr13,
        has_cnv_chr14 = srat$has_cnv_chr14,
        has_cnv_chr15 = srat$has_cnv_chr15,
        has_cnv_chr16 = srat$has_cnv_chr16,
        has_cnv_chr17 = srat$has_cnv_chr17,
        has_cnv_chr18 = srat$has_cnv_chr18,
        has_cnv_chr19 = srat$has_cnv_chr19,
        has_cnv_chr20 = srat$has_cnv_chr20,
        has_cnv_chr21 = srat$has_cnv_chr21,
        has_cnv_chr22 = srat$has_cnv_chr22
      ) |>
        tibble::rownames_to_column("barcode") |>
        dplyr::mutate(sample_id = sample_id)
    }
  ) |>
  # now combine all dataframes to make one big one
  dplyr::bind_rows()
```

@@

- Combining label transfer and CNV inference we have produced draft annotations for all 40 Wilms tumor samples in SCPCP000006
